Group meetings

### 2023-06-26 diapo/26-06-23_meeting/main.tex
Changed date
Small adjustments

\date{12/06/2023}

@@

    \centering
    \rowcolors{2}{evenRow}{oddRow}
    \begin{tabular}{ c m{4cm} c m{2cm} c }
      \rowcolor{firstRow}
      \color{white}\textbf{\#} & \centering\color{white}Task & \color{white}Done? & \color{white}Why not? & \color{white}Help? \\
      1 & Find another LSTM problem & On going & Didn't find & Yes\\
      2 & Find out what is causing the issue & Partly & I had a scale of 10 000 and reduced it to 1.5 & No\\
      3 & Find formula for approximate onChip area & No & Can be done later & No\\
      4 & Work on thesis & On going & & No\\
    \end{tabular}

>>>>

\date{26/06/2023}

@@

    \centering
    \rowcolors{2}{evenRow}{oddRow}
    \begin{tabular}{c p{0.3\textwidth} c p{0.3\textwidth} c}
      \rowcolor{firstRow}
      \color{white}\textbf{\#} & \centering\color{white}Task & \color{white}Done? & \color{white}Why not? & \color{white}Help? \\
      1 & Find another LSTM problem & On going & Didn't find & Yes\\
      2 & Find out what is causing the issue & Partly & I had a scale of 10000 and reduced it to 1.5 & No\\
      3 & Find formula for approximate onChip area & No & Can be done later & No\\
      4 & Work on thesis & On going & & No\\
    \end{tabular}
